Global SOC scenarios

### 2022-07-20 ResultNotebooks/results_SOCscenario.Rmd
update of output scripts and figure

rev         <- "rev30"
scenarios   <- c("histManagement", "constClimate-1975", "constManagement-1975", "constManagement2-1975", "constManagement-1975_constClimate-1975", "constManagement2-1975_constClimate-1975", "constManure-1975", "constResidues-1975", "constResrate-1975", "constTillage-mixedtill", "constYield-1975")

 filesNeeded  <- c("SoilCarbon.rds","Landuse.rds")
# setConfig(outputfolder = "/home/kristine/WORK/Paper/historicalsocbudget/ResultNotebooks/Data/")

@@

outputdir <- "Output/"

```

@@

for(scen in scenarios){
  print(scen)
  SoilCarbon <- read.magpie(paste0("Data/", paste0(rev,scen), "/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/", paste0(rev,scen), "/Landuse.rds"))
  SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
  SOCStock        <- toolConditionalReplace(dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2), "is.nan()",0)
  glo_SOCStock    <- mbind(glo_SOCStock, add_dimension(dimSums(SOCStock, dim=1), 
                                                       dim=3.1, nm=scen, add="scenario")) 
}

glo_SOCDebt  <- collapseNames(glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000
glo_SOCShare <- collapseNames(toolConditionalReplace(glo_SOCStock[,,"actualstate"]/glo_SOCStock[,,"naturalstate"], "is.na()",0) )

saveRDS(mbind(add_dimension(collapseNames(glo_SOCStock[,,"actualstate"]), dim=3.1, add="type", nm="stock"),
              add_dimension(              glo_SOCDebt,                    dim=3.1, add="type", nm="debt"),
              add_dimension(              glo_SOCShare,                   dim=3.1, add="type", nm="share")), 
        paste0(outputdir, "glo_SOCscenarions.rds"))
```

@@

CarbonInput  <- read.magpie(paste0("Data/", rev, "histManagement/CarbonInput.rds"))
Landuse      <- read.magpie(paste0("Data/", rev, "histManagement/Landuse.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[,,"totalC"] * Landuse, dim=c(1)))/collapseNames(dimSums(Landuse, dim=c(1)))

ci2plot <- c('above-ground residues'="ag.crop",          
             'below-ground residues'="bg.crop",          
             'manure from monogastrics'="livst_chick.crop",
             'manure from monogastrics'="livst_egg.crop",
             'manure from monogastrics'="livst_pig.crop",
             'manure from ruminants'="livst_milk.crop",  
             'manure from ruminants'="livst_rum.crop",   
             'natural litterfall wood fraction'="wood.natveg",
             'natural litterfall leaf fraction'="leaf.natveg")

glo_SOCInput <- toolAggregate(glo_SOCInput, rel=data.frame(from=ci2plot,to=names(ci2plot)), from="from", to="to", dim=3)

```

@@

glo_SOCDebt <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"debt"])

manage_scen <-  c(histManagement   = "histManagement",
                  constTillage     = "constTillage-mixedtill", 
                  constManure      = "constManure-1975",
                  constResidues    = "constResidues-1975", 
                  constManagement  = "constManagement-1975")#,
                  #constManagementNoCC = "rev26constManagement_constClimate")

@@

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF","#785EF0","#DC267F","#FE6100","#FFB000")[5:1]
input_cols  <- scen_cols[1:4]

limits <- c(-42,-34)
breaks <- c(-34, -36,- 38, -40, -42)

hSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="bottom", legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0))

hSOCinput <- ggplot(data= as.data.frame(glo_SOCInput[,seq(1975,2010,1),c(3:4,2,1)]),  aes(x = Year, y = Value, group=Data1, fill=Data1)) + geom_area() +
  labs( x = "Year", 
        y = "SOC input in tC per ha\n (global average)",
        fill="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous() +
  scale_fill_manual(values=input_cols) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="bottom", 
        legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0))

vSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1974,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

vSOCinput <- ggplot(data= as.data.frame(glo_SOCInput[,seq(1975,2010,1),c(3:4,2,1)]),  aes(x = Year, y = Value, group=Data1, fill=Data1)) + geom_area() +
  labs( x = "Year", 
        y = "SOC input in tC per ha\n (global average)",
        fill="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous() +
  scale_fill_manual(values=input_cols) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size), legend.direction="vertical")

@@

hgrid <- plot_grid(hSOCemis, hSOCinput, ncol=2, labels=c("(a)","(b)"),
                  label_fontface = "plain", label_size = 10, align="hv")

vgrid <- plot_grid(plot_grid(vSOCemis  + theme(legend.position = "none") , 
                             vSOCinput + theme(legend.position = "none"), ncol=1, labels=c("(a)","(b)"),
                             label_fontface = "plain", label_size = 10, align="v", axis="tblr"),
                   plot_grid(get_legend(vSOCemis), get_legend(vSOCinput), ncol=1,
                             label_fontface = "plain", label_size = 10, align="v"),
                   align="h")

@@

ggsave(paste0(outputdir,"Images/scenario_horiz.png"), plot=hgrid, width = 15, height = 10, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"Images/scenario_verti.png"), plot=vgrid, width = 12, height = 15, dpi = 300, units = "cm")

```

@@

glo_SOCDebt <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"debt"])

init_scen   <-  c(`histManagement.Initial-natveg`          = "rev26Initial-1901", 
                  `constManagement.Initial-natveg`         = "rev26Initial-1901_constManagement",
                  `histManagement.Initial-eq`              = "rev26Initial-0", 
                  `constManagement.Initial-eq`             = "rev26Initial-0_constManagement",
                  `histManagement.Initial-spinup1530`      = "rev26histManagement", 
                  `constManagement.Initial-spinup1530`     = "rev26constManagement")

@@

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF","#785EF0","#DC267F")
input_cols  <- scen_cols[1:4]

limits <- c(-55,-25)
breaks <- c( -30,-40,-50 )

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color    ="Initialization",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:3], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

@@

ggsave(paste0(outputdir,"Images/scenario_init.png"), plot= initSOCemis, width = 10, height = 6, dpi = 300, units = "cm")
```

```{r Plot Litter param Scenarios, out.height="6cm", out.width="18cm"}

glo_SOCDebt <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"debt"])
glo_SOCStock <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"stock"])

litter_scen <-  c(`LitterPNV-Mean` = "histManagement",
                  `LitterPNV-Grass`= "LitterPNV-PerennialGrasses", 
                  `LitterPNV-AASS` = "LitterPNV-AASS", 
                  `LitterPNV-BRCF` = "LitterPNV-BRCF", 
                  `LitterPNV-MTCF` = "LitterPNV-MTCF", 
                  `LitterPNV-BLEAF`= "LitterPNV-BLEAF",  
                  `LitterPNV-TREF` = "LitterPNV-TREF")

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF","#785EF0","#DC267F","#FE6100","#FFB000")[5:1]
input_cols  <- scen_cols[1:4]

limits <- c(-48,-40)
breaks <- c(-40, -42, -44, -46, -48)

litterSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),litter_scen]), 
                                    aes(x = Year, y = Value, group=Data1, color=Data1, size=Data1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c("red", scen_cols, "blue"), labels = names(litter_scen)) +
  scale_size_manual(values=c(1,rep(0.5, length(litter_scen)-1)), labels = names(litter_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position = "none")

litterSOCemis

limits <- c(625,705)
breaks <- c(635, 655, 675, 695)

litterSOCstock <- ggplot() + geom_line(data= as.data.frame(glo_SOCStock[,seq(1975,2010,1),litter_scen]/1000), 
                                    aes(x = Year, y = Value, group=Data1, color=Data1, size=Data1)) +
  labs( x = "Year", 
        y = "Global SOC stock\n in GtC",
        color="Litter parameterization",
        size="Litter parameterization") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c("red", scen_cols, "blue"), labels = names(litter_scen)) +
  scale_size_manual(values=c(1,rep(0.5, length(litter_scen)-1)), labels = names(litter_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0)) +
  guides(color=guide_legend(), size = guide_legend())

litterSOCstock

littergrid <- plot_grid(litterSOCemis, litterSOCstock + theme(legend.position = "none"), get_legend(litterSOCstock),
                                  ncol=3, labels=c("(a)","(b)"), axis = "l",
                                  label_fontface = "plain", label_size = 10, align="v")
littergrid

ggsave(paste0(outputdir,"Images/scenario_litter.png"), plot=littergrid, width = 18, height = 6, dpi = 300, units = "cm")

```

>>>>

rev         <- "rev30"
scenarios   <- c("histManagement", 
                 "constManagement-1975", 
                 "constManure-1975", 
                 "constResidues-1975", 
                 "constTillage-mixedtill")

 filesNeeded  <- c("SoilCarbon.rds", "Landuse.rds")
# setConfig(outputfolder = "/home/kristine/WORK/Paper/historicalsocbudget/ResultNotebooks/Data/")

@@

outputdir <- "Output/"
```

@@

for (scen in scenarios) {

  print(scen)
  SoilCarbon <- read.magpie(paste0("Data/", paste0(rev, scen), "/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/", paste0(rev, scen), "/Landuse.rds"))
  SoilCarbon[, , "naturalstate.crop"] <- SoilCarbon[, , "naturalstate.natveg"]
  SOCStock  <- toolConditionalReplace(
                 dimSums(dimSums(
                   SoilCarbon[, , "state", pmatch = TRUE], dim = 3.3) * 
                     Landuse, dim = 3.2), "is.nan()", 0)
  glo_SOCStock <- mbind(glo_SOCStock, 
                        add_dimension(dimSums(SOCStock, dim = 1),
                                      dim = 3.1, nm = scen, 
                                      add = "scenario"))
}

glo_SOCDebt  <- collapseNames(glo_SOCStock[, , "naturalstate"] - 
                                glo_SOCStock[, , "actualstate"]) / 1000
glo_SOCShare <- collapseNames(
                  toolConditionalReplace(glo_SOCStock[, , "actualstate"] /
                                           glo_SOCStock[, , "naturalstate"], 
                                         "is.na()", 0))

saveRDS(mbind(add_dimension(
                collapseNames(glo_SOCStock[, , "actualstate"]), 
                dim = 3.1, add = "type", nm = "stock"),
              add_dimension(glo_SOCDebt,                    
                dim = 3.1, add = "type", nm = "debt"),
              add_dimension(glo_SOCShare,                   
                dim = 3.1, add = "type", nm = "share")),
        paste0(outputdir, "glo_SOCscenarions.rds"))
```

@@

CarbonInput  <- read.magpie(paste0("Data/", rev, 
                                   "histManagement/CarbonInput.rds"))
Landuse      <- read.magpie(paste0("Data/", rev, 
                                   "histManagement/Landuse.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[, , "totalC"] * 
                                        Landuse, dim = c(1))) / collapseNames(dimSums(Landuse, dim = c(1)))

ci2plot <- c("above-ground residues" = "ag.crop",
             "below-ground residues" = "bg.crop",
             "manure from monogastrics" = "livst_chick.crop",
             "manure from monogastrics" = "livst_egg.crop",
             "manure from monogastrics" = "livst_pig.crop",
             "manure from ruminants" = "livst_milk.crop",
             "manure from ruminants" = "livst_rum.crop",
             "natural litterfall wood fraction" = "wood.natveg",
             "natural litterfall leaf fraction" = "leaf.natveg")

glo_SOCInput <- toolAggregate(glo_SOCInput, 
                  rel = data.frame(from = ci2plot, to = names(ci2plot)), 
                  from = "from", to = "to", dim = 3)
```

@@

glo_SOCDebt <- collapseNames(readRDS(
                 paste0(outputdir, "glo_SOCscenarions.rds"))[, , "debt"])

manage_scen <-  c(histManagement   = "histManagement",
                  constTillage     = "constTillage-mixedtill",
                  constManure      = "constManure-1975",
                  constResidues    = "constResidues-1975",
                  constManagement  = "constManagement-1975")

@@

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF", "#785EF0", "#DC267F", "#FE6100", "#FFB000")[5:1]
input_cols  <- scen_cols[1:4]

limits <- c(-42, -34)
breaks <- c(-34, -36, -38, -40, -42)
years  <- seq(1975, 2010, 1)

hSOCemis <- 
  ggplot() + 
  geom_line(data = as.data.frame(-glo_SOCDebt[, years, manage_scen]),  
            aes(x = Year, y = Value, group = Data1, color = Data1)) +
  labs(x = "Year", y = expression(paste("Global \u0394SOC in GtC")), 
       color = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous(limits = limits, breaks = breaks) +
  scale_color_manual(values = scen_cols, labels = names(manage_scen)) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size),
        legend.position = "bottom", legend.direction = "vertical",
        legend.margin = margin(-10, -10, 0, 0),
        legend.box.margin = margin(-10, -10, 0, 0))

hSOCinput <- 
  ggplot(data = as.data.frame(glo_SOCInput[, years, c(3:4, 2, 1)]),  
         aes(x = Year, y = Value, group = Data1, fill = Data1)) + geom_area() +
  labs(x = "Year", y = "SOC input in tC per ha\n (global average)", fill = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous() +
  scale_fill_manual(values = input_cols) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size),
        legend.position = "bottom",
        legend.direction = "vertical",
        legend.margin = margin(-10, -10, 0, 0),
        legend.box.margin = margin(-10, -10, 0, 0))

vSOCemis <- 
  ggplot() + geom_line(data = as.data.frame(-glo_SOCDebt[, years, manage_scen]),  
                       aes(x = Year, y = Value, group = Data1, color = Data1)) +
  labs(x = "Year", y = expression(paste("Global \u0394SOC in GtC")),
       color = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values = scen_cols, labels = names(manage_scen)) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size),
        legend.position = "right", legend.direction = "vertical")

vSOCinput <- 
  ggplot(data = as.data.frame(glo_SOCInput[, years, c(3:4, 2, 1)]),  
         aes(x = Year, y = Value, group = Data1, fill = Data1)) + geom_area() +
  labs(x = "Year", y = "SOC input in tC per ha\n (global average)", fill = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous() +
  scale_fill_manual(values = input_cols) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size), 
        legend.direction = "vertical")

@@

hgrid <- plot_grid(hSOCemis, hSOCinput, ncol = 2, labels = c("(a)", "(b)"),
                  label_fontface = "plain", label_size = 10, align = "hv")

vgrid <- plot_grid(plot_grid(vSOCemis  + theme(legend.position = "none"),
                             vSOCinput + theme(legend.position = "none"), 
                             ncol = 1, labels = c("(a)", "(b)"),
                             label_fontface = "plain", label_size = 10, 
                             align = "v", axis = "tblr"),
                   plot_grid(get_legend(vSOCemis), get_legend(vSOCinput), 
                             ncol = 1, label_fontface = "plain", 
                             label_size = 10, align = "v"),
                   align = "h")

@@

ggsave(paste0(outputdir, "Images/scenario_horiz.png"), 
       plot = hgrid, width = 15, height = 10, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "Images/scenario_verti.png"), 
       plot = vgrid, width = 12, height = 15, dpi = 300, units = "cm")
```

@@

glo_SOCStock_init <- NULL
init_scenarios    <- c("Initial-0_constManagement-1975",
                       "Initial-1901_constManagement-1975")

for (scen in init_scenarios) {
  print(scen)
  SoilCarbon <- read.magpie(paste0("Data/", rev, scen, "/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/", rev, scen, "/Landuse.rds"))
  SoilCarbon[, , "naturalstate.crop"] <- SoilCarbon[, , "naturalstate.natveg"]
  SOCStock   <- toolConditionalReplace(
                  dimSums(dimSums(
                    SoilCarbon[, , c("naturalstate", 
                                     "actualstate")], dim = 3.3) * 
                      Landuse, dim = 3.2), "is.nan()", 0)

  glo_SOCStock_init <- mbind(glo_SOCStock_init, 
                            add_dimension(dimSums(SOCStock, dim = 1),
                                          dim = 3.1, 
                                          nm = scen, 
                                          add = "scenario"))
}

glo_SOCDebt_init  <- collapseNames(glo_SOCStock_init[, , "naturalstate"] - 
                                glo_SOCStock_init[, , "actualstate"]) / 1000

saveRDS(add_dimension(glo_SOCDebt_init,                    
                      dim = 3.1, add = "type", nm = "debt_init"),
        paste0(outputdir, "glo_SOCscenarions_initConst.rds"))

glo_SOCDebt <-
  mbind(collapseNames(readRDS(
          paste0(outputdir,
                 "glo_SOCscenarions.rds"))[, , "debt"]),
        collapseNames(readRDS(
          paste0(outputdir,
                 "glo_SOCscenarions_init.rds"))[, , "debt_init"]),
        collapseNames(readRDS(
          paste0(outputdir, 
                 "glo_SOCscenarions_initConst.rds"))[, , "debt_init"]))

init_scen   <-  
  c( `histManagement.Initial-natveg`         = "Initial-1901",
    `constManagement.Initial-natveg`         = "Initial-1901_constManagement-1975",
     `histManagement.Initial-eq`             = "Initial-0",
    `constManagement.Initial-eq`             = "Initial-0_constManagement-1975",
     `histManagement.Initial-spinup1510`     = "histManagement",
    `constManagement.Initial-spinup1510`     = "constManagement-1975")

@@

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF", "#785EF0", "#DC267F")

input_cols  <- scen_cols[1:4]

limits <- c(-55, -25)
breaks <- c(-30, -40, -50)

startY <- 1965

initSOCemis <- 
  ggplot() + 
  geom_path(data = as.data.frame(-glo_SOCDebt[, seq(startY, 2010, 1), ]),
            aes(x = Year, y = Value, group = interaction(Data1, Data2), 
                linetype = Data1, color = Data2)) +
  labs(x = "Year",
        y = expression(paste("Global \u0394SOC in GtC")),
        color    = "Initialization",
        linetype = "Management") +
  scale_x_discrete(breaks = seq(startY, 2010, 5)) +
  scale_y_continuous(limits = limits, breaks = breaks) +
  scale_color_manual(values = c(scen_cols), 
                     labels = unique(gsub("(.*)\\.(.*)", "\\2", 
                                          names(init_scen)))) +
  scale_linetype_manual(values = c(1, 2), 
                        labels = unique(gsub("(.*)\\.(.*)", "\\1", 
                                             names(init_scen)))) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size),
        legend.position = "right", legend.direction = "vertical")

@@

ggsave(paste0(outputdir, "Images/scenario_init.png"), 
       plot = initSOCemis, width = 12, height = 8, dpi = 300, units = "cm")
```
